### 2018-10-20 write-up/paper/intro.tex
Rename files

\subsection{Contributions}
\begin{itemize}
    \item We have designed the \LANG\ programming language
    \item We illustrate that the design is sensible with many matrix-y examples
    \item We give a soundness proof for \LANG, using a step-indexed logical relation
    \item Incredibly simple type inference algorihtm for polymorphic fractional permissions
        \begin{itemize}
            \item Compare to Bierhof et al's \emph{Fraction Polymorphic Permission Inference},
                which uses a fancy dataflow analysis
            \item We use exactly the same unification algorithm type polymorphism does
        \end{itemize}
    \item We have an implementation - compatible with and usable from existing code!
\end{itemize}

>>>>

\lang\ is a functional programming language designed to express the APIs of
low-level linear algebra libraries (such as BLAS/LAPACK) safely and explicitly.
It does so by combining linear types, fractional permissions, runtime errors
and recursion into a small, easily understandable, yet expressive set of core
constructs. In addition to this, \lang's implementation supports several
syntactic conveniences as well as a usable integration with real-world OCaml
code.

\subsection{Contributions}
\begin{itemize}
    \item We have designed the \lang\ programming language
    \item We illustrate that the design is sensible with many matrix-y examples
    \item We give a soundness proof for \lang, using a step-indexed logical relation
    \item Incredibly simple type inference algorihtm for polymorphic fractional permissions
        \begin{itemize}
            \item Compare to Bierhof et al's \emph{Fraction Polymorphic Permission Inference},
                which uses a fancy dataflow analysis
            \item We use exactly the same unification algorithm type polymorphism does
        \end{itemize}
    \item We have an implementation - compatible with and usable from existing code!
\end{itemize}
